### 2019-05-03 monograph/thesis/chapters/introduction.tex
Moved the section related works to object_beautifier.tex
Deleted the implementation details section on introduction.tex
Renamed Research Goals to Goals on introduction.tex
Removed unrelated paragraphs from introduction.tex objective to
the introduction section.

@@

\section{\lang{Research Goals}{Objetivos de Pesquisa}}

    Beforehand due the scope limitation for a Graduation Thesis,
    we should only think about a basic, simple,
    and yet reusable core of features.

\begin{enumerate}
    \item
        A Software Product with a great Object Orientation and possibilities of extension of features,
        decent research on the state of the art.
    \item
        Ranking all code formatting classes (beautifying) applicable.
        Including a study on what does is source beautifying,
        how to do such and why.
    \item
        Establish relationships between good programming practices and efficiency in programming,
        in addition to a new tool to support programmers in order to automate the long and diverse
        programming process in teams of developers with different programming `best practices'.
    \item
        Define, determine and classify which one are good programming practices and
        perform an in\hyp{}depth study on the good practices on visual layout area,
        also known as code `Beautifying'.
    \item
        The definition of a flow pattern of development allowing teams of
        developers with different programming best practices,
        to work without intervene with each other up to start wars of `best good practices'.
    \item
        Discourse on the variety of existing tools for the support of good programming practices,
        with a comparative analysis between them,
        determining their weaknesses and strengths.
\end{enumerate}

\section{\lang{Implementation Goals}{Objetivos de Implementação}}

    Propose a unique tool that allowing several and distinct
    programming `best practices' being implemented in several programming
    languages, which can be configured and set accordingly to their wishes,
    from a single software working well behaved across all programming languages.

    Moreover, explain the differences for other softwares and the benefits
    of a unique tool, instead of several heavily different ones.

    From this point, a sketch is presented on the problem, solutions,
    information as for why to want make such software, or even why do we want to
    beautifying things:

    The difference from this proposal to remaining formatting tools,
    is the tradeoff between end\hyp{}users and developers responsibilities.
    Most tools rarely expose to end\hyp{}users their language syntax specification,
    in contrast,
    this proposal completely exposes the language to the end\hyp{}user as simple plain\hyp{}text,
    not requiring the tool to know any language syntax neither semantics.
    Moreover,
    with no syntax knowledge required,
    the tool be can used with any languages their user wishes to.

\section{\lang{Related Works}{Trabalhos Relacionados}}

\url{http://editorconfig.org/}

>>>>

\lang{%
    The difference from this proposal to remaining formatting tools,
    is the tradeoff between end\hyp{}users and developers responsibilities.
    Most tools rarely expose to end\hyp{}users their language syntax specification,
    in contrast,
    this proposal completely exposes the language to the end\hyp{}user as simple plain\hyp{}text,
    not requiring the tool to know any language syntax neither semantics.
    Moreover,
    with no syntax knowledge required,
    the tool be can used with any languages their user wishes to.
}{%

}

@@

\section{\lang{Goals}{Objetivos}}

\lang{%
    Beforehand due the scope limitation for a Graduation Thesis,
    we should only think about a basic, simple,
    and yet reusable core of features.
}{%
    Devido ao trabalho tratar-se de uma tese de graduação,
    limita~=se seu escopo de trabalho a somente realizara criação de um núcleo reduzido de recursos.
}

\lang{%
\begin{enumerate}
    \item
        A Software Product with a great Object Orientation and possibilities of extension of features,
        decent research on the state of the art.
    \item
        Ranking all code formatting classes (beautifying) applicable.
        Including a study on what does is source beautifying,
        how to do such and why.
    \item
        Establish relationships between good programming practices and efficiency in programming,
        in addition to a new tool to support programmers in order to automate the long and diverse
        programming process in teams of developers with different programming `best practices'.
    \item
        Define, determine and classify which one are good programming practices and
        perform an in\hyp{}depth study on the good practices on visual layout area,
        also known as code `Beautifying'.
    \item
        The definition of a flow pattern of development allowing teams of
        developers with different programming best practices,
        to work without intervene with each other up to start wars of `best good practices'.
    \item
        Discourse on the variety of existing tools for the support of good programming practices,
        with a comparative analysis between them,
        determining their weaknesses and strengths.
\end{enumerate}
}{%
    Enumerar e
    explicar as ferramentas de formatação de código~=fonte e
    realizar o desenvolvimento de uma nova ferramenta de formatação de código~=fonte que seja extensível.
}

\subsection{Objetivos Específicos}

\lang{%
    Propose a unique tool that allowing several and distinct
    programming `best practices' being implemented in several programming
    languages, which can be configured and set accordingly to their wishes,
    from a single software working well behaved across all programming languages.
}{%
    Propor uma ferramenta que permita várias e
    diferentes linguagens de programação sejam formatadas utilizando o mesmo conjunto de configurações.
    Utilizando esta única ferramenta,
    novas linguagens podem ser configuradas e
    adicionadas de acordo com a vontade de seus usuários.
}

\lang{%
    Moreover, explain the differences for other softwares and the benefits
    of a unique tool, instead of several heavily different ones.
    From this point, a sketch is presented on the problem, solutions,
    information as for why to want make such software, or even why do we want to
    beautifying things:
}{%
    E explicar como esta nova ferramenta difere das demais já existentes,
    e qual as vantagens de ter uma ferramenta para formatar todas as linguagens de programação,
    ao contrário de ter uma ferramenta para cada linguagem.
}

\section{ESTRUTURAÇÃO DO TEXTO}

No capítulo 2,
será mostrado um revisão da literatura sobre os conceitos básicos.

TODO.
